\song{Yogi Bear (\textit{404})}{The sun is going up and down}

            I know someone you dont know,  \\
            Yogi, Yogi, \\
            I know someone you dont know,  \\
            Yogi, Yogi bear. \\
            Yogi, Yogi bear, Yogi, Yogi bear. \\
            I know someone you dont know,  \\
            Yogi Yogi bear. \\
\hspace{10mm} \\
            Yogi has a little friend, Bobo, Bobo.  \\
            Yogi has a little friend, Bobo, Bobo bear.  \\
            Bobo, Bobo bear, Bobo, Bobo bear.  \\
            Yogi has a little friend, Bobo, Bobo bear. \\
\hspace{10mm} \\
            Yogi has a girlfriend, Cindy, Cindy.  \\
            Yogi has a girlfriend, Cindy, Cindy bear.  \\
            Cindy, Cindy bear, Cindy, Cindy bear.  \\
            Yogi has a girlfriend, Cindy, Cindy bear. \\
\hspace{10mm} \\
            Cindy likes it from behind, \\
            frombe, frombe.  \\
            Cindy likes it from behind,  \\
            frombe, from behind. \\
            Frombe, from behind, \\
            frombe from behind. \\
            Cindy likes it from behind, \\
            frombe, from behind. \\
\hspace{10mm} \\
            Yogi has an enemy, ranger, ranger. \\
            Yogi has an enemy, ranger, ranger Smith.  \\
            Ranger, ranger Smith, \\
            ranger, ranger Smith.  \\
            Yogi has an enemy, \\
            ranger, ranger Smith. \\
\hspace{10mm} \\
            Ranger Smith fucks animals,  \\
            animals, animals.  \\
            Ranger Smith fucks animals, \\
            ani, animals. \\
            Ani, animals, ani, animals.  \\
            Ranger Smith fucks animals, \\
            ani, animals. \\
\hspace{10mm} \\
            Yogi has a Swedish friend, Puppe, Puppe. \\
            Yogi has a Swedish friend, \\
            Puppe Guppelström. \\
            Puppe Guppelström, \\
            Puppe Guppelström. \\
            Yogi has a Swedish friend, \\
            Puppe Guppelström. \\
\hspace{10mm} \\
            \begin{comment} Lisäsäkeistöt: \\
\hspace{10mm} \\
            Betsy likes it in the group, gangbang, gangbang. \\
            Betsy likes it in the group, gang-ga gang gangbang. \\
\hspace{10mm} \\
            Yogi’s into whips and chains, kinky, kinky. \\
            Yogi’s into whips and chains, kinky, kinky bear. \\
\hspace{10mm} \\
            Yogi likes it in the fridge, polar, polar. \\
            Yogi likes it in the fridge, polar, polar bear. \\
\hspace{10mm} \\
            Yogi likes them dead and cold, necro, necro. \\
            Yogi likes them dead and cold, necrophilic bear. \\
\hspace{10mm} \\
            Yogi likes it young and sweet, pedo, pedo. \\
            Yogi likes it young and sweet, pedo, pedobear. \\
\hspace{10mm} \\
            Yogi has a seven inch, seven, seven. \\
            Yogi has a seven inch, seven inch cock. \\
\hspace{10mm} \\
            Yogi sits on Santa’s lap, feelin’, feelin’. \\
            Yogi sits on Santa’s lap, feelin’ something hard. \\
\hspace{10mm} \\
            Yogi likes girl’s underwear, panty, sniffer. \\
            Yogi likes girl’s underwear, panty sniffer bear. \\
\hspace{10mm} \\
            Yogi doesn't shave at all, grizzly, grizzly. \\
            Yogi doesn't shave at all, grizzly, grizzly bear. \\
\hspace{10mm} \\
            Yogi gets what he deserves, HI, HI. \\
            Yogi gets what he deserves, HI, HIV. \\
\hspace{10mm} \\
            Cindy gets what she deserves, pregnan, pregnan. \\
            Cindy gets what she deserves, pregnan, pregnancy. \\
\hspace{10mm} \\
            Michael likes it underage, under, under. \\
            Michael likes it underage, under, underage. \\
\end{comment}